Robust and Efficient CSI Compression Using CLLWCsiNet in Noisy MIMO Environments

### 2025-04-16 Revise-version.tex
txs auto checkin

>>>>

\begin{figure*}[t]
	\centering
	\begin{tikzpicture}[
		node distance=0.5cm and 0.8cm,
		block/.style={draw, fill=white, rectangle, minimum width=2cm, minimum height=0.8cm, font=\footnotesize, align=center, rounded corners=3pt},
		conv/.style={block, fill=orange!20},
		compress/.style={block, fill=blue!20},
		arrow/.style={->, >=stealth', semithick}
		]

		% Input
		\node[compress] (input) {Input CSI \\ $2{\times}32{\times}32$};

		% Encoder Paths
		\node[conv, right=of input] (conv1x7) {Conv $1{\times}7$ \\ $2{\rightarrow}2$};
		\node[conv, below=of conv1x7] (conv1x5) {Conv $1{\times}5$ \\ $2{\rightarrow}2$};
		\node[conv, below=of conv1x5] (conv1x3) {Conv $1{\times}3$ \\ $2{\rightarrow}2$};

		% Concatenation
		\node[block, right=2cm of conv1x5] (concat) {Feature Fusion \\ $6{\rightarrow}2$};

		% Latent Space Entry
		\node[compress, right=of concat] (reshape) {Reshape \\ $2{\rightarrow}64$};
		\node[conv, right=of reshape] (encoder1) {Conv $1{\times}7$ \\ $64{\rightarrow}32$};
		\node[conv, right=of encoder1] (encoder2) {Conv $1{\times}7$ \\ $32{\rightarrow}16$};

		% Continuation Marker
		\node[below=0.1cm of encoder2, font=\footnotesize] {$\downarrow$ Compression Ratio: $\gamma=4/8/16$ $\downarrow$};

		% Arrows
		\foreach \i in {conv1x7, conv1x5, conv1x3} 
		\draw[arrow] (input) -- (\i);

		\foreach \i in {conv1x7, conv1x5, conv1x3} 
		\draw[arrow] (\i) -- (concat);

		\draw[arrow] (concat) -- (reshape);
		\draw[arrow] (reshape) -- (encoder1);
		\draw[arrow] (encoder1) -- (encoder2);

		% Part label
		\node[above=0.1cm of input, font=\small\bfseries] {Encoder Stage};
	\end{tikzpicture}

	\vspace{-3mm} % Reduces space between figures

	% Lower Half (Decoder) - MOVED UP
	\begin{tikzpicture}[
		node distance=0.5cm and 0.8cm,
		block/.style={draw, fill=white, rectangle, minimum width=2cm, minimum height=0.8cm, font=\footnotesize, align=center, rounded corners=3pt},
		conv/.style={block, fill=orange!20},
		residual/.style={block, fill=green!20},
		compress/.style={block, fill=blue!20},
		arrow/.style={->, >=stealth', semithick}
		]

		% Latent Space Exit
		\node[compress] (decoder1) {Conv $1{\times}7$ \\ $16{\rightarrow}32$};
		\node[conv, right=of decoder1] (decoder2) {Conv $1{\times}7$ \\ $32{\rightarrow}64$};
		\node[compress, right=of decoder2] (reshape2) {Reshape \\ $64{\rightarrow}2$};

		% RefineNet
		\node[residual, above right=0.5cm and 1cm of reshape2] (refine1) {RefineNet \\ $1{\times}7+1{\times}5$};
		\node[residual, right=of refine1] (refine2) {RefineNet \\ $1{\times}7+1{\times}5$};

		% Output
		\node[compress, right=of refine2] (output) {Output CSI \\ $2{\times}32{\times}32$};

		% Continuation Marker
		\node[above=0.1cm of decoder1, font=\footnotesize] {$\uparrow$ Latent Representation $\uparrow$};

		% Arrows
		\draw[arrow] (decoder1) -- (decoder2);
		\draw[arrow] (decoder2) -- (reshape2);
		\draw[arrow] (reshape2) -- (refine1);
		\draw[arrow] (refine1) -- (refine2);
		\draw[arrow] (refine2) -- (output);

		% Skip connections
		\draw[arrow, dashed] (decoder1.west) to[out=180,in=180] node[pos=0.6, left] {\scriptsize Noise} (-1.5,0) to (decoder1.west);
		\draw[arrow, dashed] (reshape2) to[bend left] (refine2);

		% Part label
		\node[above=0.6cm of decoder1, font=\small\bfseries] {Decoder Stage};
	\end{tikzpicture}

	\caption{Complete CLLWCsiNet architecture: (Upper) Encoder stage with multi-scale feature extraction and latent space compression. (Lower) Decoder stage with reconstruction and denoising refinement. The $\gamma$ denotes compression ratio options.}
	\label{fig:complete_arch}
\end{figure*}
